Report on the Second Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE2)

### 2015-06-26 WSSSPE2_report/WSSSPE2_review.tex
undoing a change

Neil Chue Hong is the Director of the Software Sustainability Institute (SSI) in the
United Kingdom (UK). The SSI was founded to support the UK's research software
community by cultivating better, more sustainable software to enable
world-class research. Chue Hong's keynote started by making the point
that the use of -- and reliance on -- software is pervasive in all areas of
world-leading research, showing examples from disciplines as diverse as
humanities and high-energy physics, quoting Kerstin Kleese Van Dam of the
Pacific Northwestern National Laboratory via a petition
campaign\footnote{\url{http://tinyurl.com/nkn5tnv}}
%https://www.change.org/p/everyone-in-the-research-community-we-must-accept-that-software-is-fundamental-to-research-or-we-will-lose-our-ability-to-make-groundbreaking-discoveries}}
at change.org, ``\emph{Today there are very few science areas left which do not
rely on IT and thus software for the majority of their research work. More
importantly key scientific advances in experimental and observational science
would have been impossible without better software.}'' He also cited Daniel
Katz, Software Infrastructure for Sustained Innovation (SI2) Program Director of
the NSF, ``\emph{Scientific discovery and innovation are advancing along
fundamentally new pathways opened by development of increasingly sophisticated
software. Software is an integral enabler of computation, experiment and theory,
and directly responsible for increased scientific productivity and enhancement
of researchers' capabilities.}''

>>>>

Neil Chue Hong is the Director of the Software Sustainability Institute (SSI) in the
United Kingdom (UK). The SSI was founded to support the UK's research software
community by cultivating better, more sustainable research software to enable
world-class research. Chue Hong's keynote started by making the point
that the use of -- and reliance on -- software is pervasive in all areas of
world-leading research, showing examples from disciplines as diverse as
humanities and high-energy physics, quoting Kerstin Kleese Van Dam of the
Pacific Northwestern National Laboratory via a petition
campaign\footnote{\url{http://tinyurl.com/nkn5tnv}}
%https://www.change.org/p/everyone-in-the-research-community-we-must-accept-that-software-is-fundamental-to-research-or-we-will-lose-our-ability-to-make-groundbreaking-discoveries}}
at change.org, ``\emph{Today there are very few science areas left which do not
rely on IT and thus software for the majority of their research work. More
importantly key scientific advances in experimental and observational science
would have been impossible without better software.}'' He also cited Daniel
Katz, Software Infrastructure for Sustained Innovation (SI2) Program Director of
the NSF, ``\emph{Scientific discovery and innovation are advancing along
fundamentally new pathways opened by development of increasingly sophisticated
software. Software is an integral enabler of computation, experiment and theory,
and directly responsible for increased scientific productivity and enhancement
of researchers' capabilities.}''
